---
title: "Introduction"
---



# Background

R is an open source and free software environment for statistical computing and graphics.
It can be readily downloaded from <http://cran.ma.imperial.ac.uk/> or other mirror sites.
A position paper on its ability to meet FDA and EME regulatory requirements for Clinical Trials  is provided in the R-FDA.pdf appendix and the R-SDLC.pdf gives an overview of the development cycle.
Internal tools are provided to check that an installation is successful. These function by running pre-written scripts to a) check that they run without errors b) the output that is produced matches up to pre-saved output files supplied with the download.

<https://cran.ma.imperial.ac.uk/doc/manuals/r-release/R-admin.html#Testing-a-Unix_002dalike-Installation>

# R System

Local CRSid: `r Sys.getenv("CRSID")`

```{r system}
R.version
Sys.info()
```


# Tests

We now provide links to code and output that comes from running 

* [Base](test_base.qmd) tests with the  functions `tools::testInstalledBasic` and `tools::testInstalledPackages` for the software that ships directly without any add-ons
* The [recommended](test_recommended.qmd) packages, that are included as default add-ons  using `tools::testInstalledPackages`
* Our [bespoke](test_bespoke.qmd) in-house choice of further add-on packages  with `tools::testInstalledPackage`  (note the extra "s" or not in the function name)


# Post processing summary

This data table shows what _should_ have been tested, and what has actually succeeded (0 is Success, 1 is Fail), along with date stamps

```{r}
load("log.Rdata")
log
```